First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-02-16 eg6-letters/coherent/dvcs_he4_prl.tex
correct the contract nuber in the acknowledgements.

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}
\newcommand*{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand*{\ODUindex}{4}
\newcommand*{\INFNGE}{INFN, Sezione di Genova, 16146 Genova, Italy}
\newcommand*{\INFNGEindex}{5}
\newcommand*{\UTFSM}{Universidad T\'{e}cnica Federico Santa Mar\'{i}a, Casilla 110-V Valpara\'{i}so, Chile}
\newcommand*{\UTFSMindex}{6}
\newcommand*{\MISS}{Mississippi State University, Mississippi State, MS 39762-5167}
\newcommand*{\MISSindex}{7}
\newcommand*{\VIRGINIA}{University of Virginia, Charlottesville, Virginia 22901}
\newcommand*{\VIRGINIAindex}{8}

@@

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {R.~Dupr\'{e}} 
\email[corresponding author: ]{dupre@ipno.in2p3.fr}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {K.~Hafidi} 
\affiliation{\ANL}
\author{S.~Stepanyan}
\affiliation{\JLAB}
\author {S.~Bultmann} 
\affiliation{\ODU}
\author{R.~De~Vita} 
\affiliation{\INFNGE}
\author {A.~El~Alaoui} 
\affiliation{\ANL}
\affiliation{\UTFSM}
\author {L.~El~Fassi} 
\affiliation{\MISS}
\author{H.~Egiyan}
\affiliation{\JLAB}
\author{F.X.~Girod} 
\affiliation{\JLAB}
\author{S.~Liuti} 
\affiliation{\VIRGINIA}
\author {B.~Torayev} 
\affiliation{\ODU}
\author {E.~Voutier} 
\affiliation{\ORSAY}

@@

We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
Lab for making this experiment possible. This work is supported by the U.S.  
Department of Energy, Office of Science, Office of Nuclear Physics contract 
DE-AC05-06OR23177.

>>>>

\newcommand*{\ANL}{Argonne National Laboratory, Argonne, Illinois 60439}
\newcommand*{\ANLindex}{1}
\affiliation{\ANL}
\newcommand*{\ORSAY}{Institut de Physique Nucl\'eaire, CNRS/IN2P3 and Universit\'e Paris Sud, Orsay, France}
\newcommand*{\ORSAYindex}{2}
\affiliation{\ORSAY}
\newcommand*{\JLAB}{Thomas Jefferson National Accelerator Facility, Newport News, Virginia 23606}
\newcommand*{\JLABindex}{3}
\affiliation{\JLAB}
\newcommand*{\ODU}{Old Dominion University, Norfolk, Virginia 23529}
\newcommand*{\ODUindex}{4}
\newcommand*{\INFNGE}{INFN, Sezione di Genova, 16146 Genova, Italy}
\newcommand*{\INFNGEindex}{5}
\newcommand*{\UTFSM}{Universidad T\'{e}cnica Federico Santa Mar\'{i}a, Casilla 110-V Valpara\'{i}so, Chile}
\newcommand*{\UTFSMindex}{6}
\newcommand*{\MISS}{Mississippi State University, Mississippi State, MS 39762-5167}
\newcommand*{\MISSindex}{7}
\newcommand*{\VIRGINIA}{University of Virginia, Charlottesville, Virginia 22901}
\newcommand*{\VIRGINIAindex}{8}
\newcommand*{\VIRGINIATECH}{Virginia Polytechnic Institute and State University, Blacksburg, Virginia, 24061}
\newcommand*{\VIRGINIATECHindex}{9}

@@

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {R.~Dupr\'{e}} 
\email[corresponding author: ]{dupre@ipno.in2p3.fr}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {K.~Hafidi} 
\affiliation{\ANL}
\author{S.~Stepanyan}
\affiliation{\JLAB}
\author {S.~Bultmann} 
\affiliation{\ODU}
\author{R.~De~Vita} 
\affiliation{\INFNGE}
\author {A.~El~Alaoui} 
\affiliation{\ANL}
\affiliation{\UTFSM}
\author {L.~El~Fassi} 
\affiliation{\MISS}
\author{H.~Egiyan}
\affiliation{\JLAB}
\author{F.X.~Girod} 
\affiliation{\JLAB}
\author{D.~Jenkins}
\affiliation{\VIRGINIATECH}
\author{S.~Liuti} 
\affiliation{\VIRGINIA}
\author{Y.~Perrin}
\affiliation{\ORSAY}
\author {B.~Torayev} 
\affiliation{\ODU}
\author {E.~Voutier} 
\affiliation{\ORSAY}

@@

We acknowledge the staff of the Accelerator and Physics Divisions at Jefferson 
Lab for making this experiment possible. This work is supported by the U.S.  
Department of Energy, Office of Science, Office of Nuclear Physics, under 
contract DE-AC02-06CH11357.
